Long term cloud enhancement events of global solar irradiance over Thessaloniki

### 2024-05-26 article/article.Rmd
Commit 2024-05-26 22:14

---
title: Downward shortwave solar irradiance enhancement by clouds.

@@

- Phenomenon
- Effects
- bibliography
- our approach
- our results

CE: cloud enhancement cases one minute

@@

$\text{GHI}_\text{CSm}$: modeled clear sky one minute global horizontal irradiance

@@

The shortwave solar irradiance, reaching Earth's surface, is the main energy source
of the atmosphere and biosphere and drives and governs the climate [@Gray2010].  It
has direct practical application, in different industries, like energy production and
agriculture method.  The variability of its intensity, can cause difficulties in
predicting the yield, and designing the specifications of the appropriate equipment.
A lot of research has been focused on predicting the renewable energy production in a
fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).

A big aspect of this variability is the interaction with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can enhance
the total shortwave irradiance reaching the ground. This effect, can locally increase
the observed total shortwave irradiance higher than the expected clear sky irradiance
[see references therein].

>>>>

---
title: Long term cloud enhancement events of global solar irradiance over Thessaloniki

@@

We studied the enhancement of the global horizontal irradiance (GHI), over Thessaloniki, 
for the period 1993 -- 2023, on one minute average records.
We identify the cloud enhancement events (CE), by creating an appropriate clear sky
irradiance reference with the use of a radiation transfer model, and aerosol optical 
depth (AOD) data, from the AERONET, and a collocated Brewer photospectrometer.
We found that there is a trend of CE cases of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$,
and a
mean total energy change, of the CE events by
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$
with the peak of the CE events are observed during May and June.
An analysis of the total duration of CE events, showed that durations longer than 
5 minutes are very rare, with exceptions lasting over an hour.
We have detected enhancements over the total solar irradiance, without exceeding the
maximum values reported for other sites, with more favorable CE conditions.

\  
\  
CE: cloud enhancement cases one minute

@@

$\text{GHI}_\text{CSm}$: modelled clear sky one minute global horizontal irradiance

@@

The shortwave solar irradiance, reaching Earth's surface, is the main energy source
of the atmosphere and the biosphere, and drives and governs the climate [@Gray2010].  It
has direct practical application, in industries like energy and
agricultural production. The variability of its intensity, can cause difficulties in
predicting the yield, and designing the specifications of the appropriate equipment.
Significant portion of research has been focused on predicting the renewable energy production in a
fine timescale and in near real-time (for a review see @Inman2013; @Graabak2016).

A big aspect of this variability is the interaction of GHI with the clouds. In general,
clouds absorb part of the solar irradiance, but under certain conditions, can enhance
the total shortwave irradiance reaching the ground. This effect, can locally increase
the observed GHI, even higher than the expected clear sky irradiance
[see references therein].
